\documentclass[11pt, letterpaper]{article}
    \usepackage{titlesec}
    \usepackage{titling}
    \usepackage{enumitem}
    \usepackage[margin=0.5in]{geometry}
    \usepackage{fontawesome}
    \usepackage[misc]{ifsym}

\setlength{\parindent}{0pt}

\titleformat{\section}
    {\large\bfseries\vspace{0.1em}}{}{0em}{}
    [\titlerule]

\titlespacing{\section}
    {0em}{0.5em}{0.5em}

\titleformat{\subsection}
    {\bfseries\large}{}{0em}{}

\titlespacing{\subsection}
    {0em}{0.75em}{0.25em}

\titleformat{\subsubsection}[runin]
    {\bfseries}{}{0em}{}[:]

\titlespacing{\subsubsection}
    {0em}{0.25em}{0.5em}

\renewcommand{\maketitle} {
    \thispagestyle{empty}
    \begin{center}    
        {\huge\bfseries \theauthor}

        \vspace{.5em}

        \quad \quad \quad \quad
        \faGithub \quad github.com/ss9415 \quad 
        \Letter \quad  shantanav@sauravmakes.tech \quad
        \faLinkedin \quad linkedin.com/in/shantanav \quad  

    \end{center}
}


\begin{document}

    \author{Shantanav Saurav}
    \maketitle

    \section{Objective}
        Passionate software engineer seeking a software developer co-op position. 
        Available May 2021 - August 2021.
    \section{Education}
        \textbf{Rochester Institute of Technology - B.S. Software Engineering \hfill May 2023}

    \section{Skills}
        \textbf{Tools:}
            Python, Java, C, PostreSQL, React.js, Node.js, LaTeX Git, ReSTful, Agile,
            Test Driven Development, Web Scraping, Shell Scripting, Cloud Computing \newline
        \textbf{Languages:}
            \emph{Fluent:} English, French, Hindi 
            \emph{Conversational:} American Sign Language

    \section{Projects}
        \subsection{Tech Talk Lecture Series}
            Developed and presented a series of informative talks on various topics in technology, software 
            development, and personal software process Wrote practice exercises and games for attendees to 
            interact with the subject matter. Had an average of 15 attendees at every talk.
            \subsubsection{Tools}
                Vim, Shell Scripting, Cloud Computing with Azure

        \subsection{LeagueBot - Personal Project}
            Created a Discord bot that fetches information on updates to the video game League of Legends 
            that web scraped the Riot Games website for patch information. Consolidated relevant information 
            and links into a Discord embed for user convenience, incorporating images and videos from the 
            patch notes to make the embed visually appealing.
            \subsubsection{Tools}
                Python, Web Scraping, ReSTful

        \subsection{Web Checkers - Team Project}
            Designed, build, and tested a browser-based online competitive checkers game for multiple players. 
            Worked with a team to implement an agile workflow and design and develop the product over three 
            releases. Thoroughly tested the code, and achieved 96\% code coverage with unit testing.
            \subsubsection{Tools}
                Java, ReSTful, Git, Agile, Test Driven Development

        \subsection{Radio Lyric Checker - Personal Project}
            Developed a python program to query the Spotify API for playlist data, and use the Genius Lyrics
            API to check for curse words in the lyrics of the song to determine their eligibility for radio
            airplay. 
            \subsubsection{Tools}
                Python, ReSTful APIs

    \section{Leadership}
        \subsection{Teaching Assistant - Rochester Institute of Technology \hfill January 2021 - Present}
            Adapted classroom environments to the challenges presented by COVID 19 by facilitating in-person
            instruction for entirely remote professors. Presented supplemental material to students by running 
            lectures outside of class time, and stood in for professors and ran lectures in their absence. 
            Graded over 700 student assignments.

        \subsection{Assistant Programming Director - WITR 89.7FM \hfill August 2020 - Present}
            Set up and schedule on air events and shows, alongside structured automatic programming clocks to 
            ensure quality broadcasts at all hours of the day.

        \subsection{Head of Technology - Society of Software Engineers \hfill August 2020 - Present}
            Build and maintain the organization's tech stack and repositories, while playing an active role 
            in the leadership of the organization. Spearheaded the complete replacement and modernization of 
            the organization's entire tech stack.

\end{document}

